Constructing Quotient Inductive-Inductive Types

### 2018-11-02 paper.tex
page break fixes
Capitalize subsections & add ACM CCS

\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011008</concept_id>
<concept_desc>Software and its engineering~General programming languages</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003457.10003521.10003525</concept_id>
<concept_desc>Social and professional topics~History of programming languages</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~General programming languages}
\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

@@

\subsection{Natural numbers}
\label{sec:naturals}

@@

\subsection{Contexts and types}
\label{sec:conty}

@@

\subsection{Overview of the rest of the paper}

@@

\subsection{Related work}
\label{sec:related-work}

@@

\subsection{The syntax}
\label{sec:syntax}

@@

As an example of using the substitution calculus, we prove the functor
laws for terms using equational reasoning.
\begin{alignat*}{15}
  & [\id] && : && t[\id] &&                      && && \hspace{6em} [\circ] && : && t[\sigma\circ\delta] \\
  & && && && && {\rhd\beta_2}^{-1}                && && && && && {\rhd\beta_2}^{-1} \\
  & && = \,\, && \pi_2\,(\id, t[\id]) &&         && && && = \,\, && \pi_2\,(\sigma\circ\delta, t[\sigma\circ\delta]) \\
  & && && && && {\idl}^{-1}                       && && && && && {\idl}^{-1} \\
  & && = \,\, && \pi_2\,(\id\circ\id, t[\id])    && && && && = \,\, && \pi_2\,(\id\circ(\sigma\circ\delta), t[\sigma\circ\delta]) \\
  & && && && && {,\circ}^{-1}                    && && && && && {,\circ}^{-1} \\
  & && = \,\, && \pi_2\,((\id, t)\circ\id) &&    && && && = \,\, && \pi_2\,((\id, t)\circ(\sigma\circ\delta)) \\
  & && && && && \idr                             && && && && && \ass^{-1} \\
  & && = \,\, && \pi_2\,(\id, t) &&              && && && = \,\, && \pi_2\,(((\id, t)\circ\sigma)\circ\delta) \\
  & && && && && {\rhd\beta_2}                    && && && && && {,\circ} \\
  & && = \,\, && t &&                            && && && = \,\, && \pi_2\,((\id\circ\sigma, t[\sigma])\circ\delta) \\
  & && && &&                                     && && && && && && {,\circ} \\
  & && && &&                                     && && && = \,\, && \pi_2\,((\id\circ\sigma)\circ\delta, t[\sigma][\delta]) \\
  & && && &&                                     && && && && && && {\rhd\beta_2} \\
  & && && &&                                     && && && = \,\, && t[\sigma][\delta]
\end{alignat*}

@@

\subsection{Example signatures}

@@

\subsection{Defining functions from the syntax}
\label{sec:syntaxfunctions}

@@

@@

\subsection{CwF$^\K_{\Eq}$s of algebras}
\label{sec:cwfalg}

@@

\subsection{Equivalence of initiality and induction}
\label{sec:initind}

@@

\subsection{The CwF$^\K_{\Eq}$ model of the theory of signatures}
\label{sec:cwfmodel}

>>>>

\documentclass[acmsmall,screen]{acmart}

@@

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003752.10003790.10011740</concept_id>
<concept_desc>Theory of computation~Type theory</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Type theory}
%% End of generated code

@@

\subsection{Natural Numbers}
\label{sec:naturals}

@@

\subsection{Contexts and Types}
\label{sec:conty}

@@

\subsection{Overview of the Rest of the Paper}

@@

\subsection{Related Work}
\label{sec:related-work}

@@

\subsection{The Syntax}
\label{sec:syntax}

@@

As an example of using the substitution calculus, we prove the functor
laws for terms using equational reasoning. We use the same names for
these laws as for type subsitution: ${[\id]}$ and ${[\circ]}$.
\begin{alignat*}{15}
  & [\id] && : && t[\id] \\
  & && && && && {\rhd\beta_2}^{-1} \\
  & && = \,\, && \pi_2\,(\id, t[\id]) \\
  & && && && && {\idl}^{-1} \\
  & && = \,\, && \pi_2\,(\id\circ\id, t[\id]) \\
  & && && && && {,\circ}^{-1} \\
  & && = \,\, && \pi_2\,((\id, t)\circ\id) \\
  & && && && && \idr \\
  & && = \,\, && \pi_2\,(\id, t) \\
  & && && && && {\rhd\beta_2} \\
  & && = \,\, && t \\
  \\
  \\
  & [\circ] && : && t[\sigma\circ\delta] \\
  & && && && \hspace{2em} && {\rhd\beta_2}^{-1} \\
  & && = \,\, && \pi_2\,(\sigma\circ\delta, t[\sigma\circ\delta]) \\
  & && && && && {\idl}^{-1} \\
  & && = \,\, && \pi_2\,(\id\circ(\sigma\circ\delta), t[\sigma\circ\delta]) \\
  & && && && && {,\circ}^{-1} \\
  & && = \,\, && \pi_2\,((\id, t)\circ(\sigma\circ\delta)) \\
  & && && && && \ass^{-1} \\
  & && = \,\, && \pi_2\,(((\id, t)\circ\sigma)\circ\delta) \\
  & && && && && {,\circ} \\
  & && = \,\, && \pi_2\,((\id\circ\sigma, t[\sigma])\circ\delta) \\
  & && && && && {,\circ} \\
  & && = \,\, && \pi_2\,((\id\circ\sigma)\circ\delta, t[\sigma][\delta]) \\
  & && && && && {\rhd\beta_2} \\
  & && = \,\, && t[\sigma][\delta]
\end{alignat*}

@@

\subsection{Example Signatures}

@@

\subsection{Defining Functions from the Syntax}
\label{sec:syntaxfunctions}

@@

\pagebreak

@@

\subsection{CwF$^\K_{\Eq}$s of Algebras}
\label{sec:cwfalg}

@@

\subsection{Equivalence of Initiality and Induction}
\label{sec:initind}

@@

\subsection{The CwF$^\K_{\Eq}$ Model of the Theory of Signatures}
\label{sec:cwfmodel}
